Cell Decompositions for Rank Two Quiver Grassmannians

### 2019-07-01 Grassmannian_cells.tex
Small edit
revised version submitted to Math.Zeit.

%\title[Cell Decompositions for Quiver Grassmannians]{Cell Decompositions for Rank Two Quiver Grassmannians}

@@

\begin{document}
%\setcounter{tocdepth}{2}

%\maketitle%\tableofcontents

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quiver Covering Theory}
\label{sec:covering}
\noindent
We refer to \cite{gab} for an introduction to covering theory.
Let $Q$ be an acyclic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:s(\alpha)\to t(\alpha)$.
A $\CC$-representation $X$ of $Q$ consists of a collection of $\CC$-vector spaces $X_i$ for $i\in Q_0$ and a collection of $\CC$-linear maps $X_\alpha:X_{s(\alpha)}\to X_{t(\alpha)}$ for $\alpha\in Q_1$.
The dimension vector of $X$ is $\udim X:=(\dim X_i)_{i\in Q_0}\in\NN^{Q_0}$.
Given $\CC$-representations $X$ and $Y$ of $Q$, a morphism $f:X\to Y$ is a collection of $\CC$-linear maps $f_i:X_i\to Y_i$ for $i\in Q_0$ satisfying $f_{t(\alpha)}\circ X_\alpha=Y_\alpha\circ f_{s(\alpha)}$ for each $\alpha\in Q_1$.
We write $\rep Q$ for the hereditary abelian category of finite-dimensional $\C$-representations of $Q$, and we assume in the following that all representations are finite-dimensional.

@@

  Since the map $ev_V$ is irreducible, $f$ is either a section or $h$ a retraction.  As $h$ is injective by the Snake lemma, it cannot be a retraction. It follows that $f$ is a section and thus $g$ a retraction. Thus we find a morphism $g':X\to E$ such that $g\circ g'=\mathrm{id}_X$. We obtain
	$$\iota=\iota\circ\mathrm{id}_X=\iota\circ g\circ g'=\pi_{m+1}^V \circ h\circ g',$$i.e. $\iota$ factors through $P_{m+1}$,	and the claim follows from Lemma~\ref{le:preprojective subs}.
  %We proceed by induction on $m$.
  %When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{\cH_m} V,1)$.
  %In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le\codim_{\cH_m} V$.

>>>>

\title{Cell Decompositions for Rank Two Quiver Grassmannians}

@@

\begin{document}
\setcounter{tocdepth}{2}

\maketitle%\tableofcontents

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quiver Covering Theory}
\label{sec:covering}
\noindent
We refer to \cite{gab} for an introduction to quiver covering theory.
Let $Q$ be an acyclic quiver with vertices $Q_0$ and arrows $Q_1$ which we denote by $\alpha:s(\alpha)\to t(\alpha)$.
A $\CC$-representation $X$ of $Q$ consists of a collection of $\CC$-vector spaces $X_i$ for $i\in Q_0$ and a collection of $\CC$-linear maps $X_\alpha:X_{s(\alpha)}\to X_{t(\alpha)}$ for $\alpha\in Q_1$.
The dimension vector of $X$ is $\udim X:=(\dim X_i)_{i\in Q_0}\in\NN^{Q_0}$.
Given $\CC$-representations $X$ and $Y$ of $Q$, a morphism $f:X\to Y$ is a collection of $\CC$-linear maps $f_i:X_i\to Y_i$ for $i\in Q_0$ satisfying $f_{t(\alpha)}\circ X_\alpha=Y_\alpha\circ f_{s(\alpha)}$ for each $\alpha\in Q_1$.
We write $\rep Q$ for the hereditary abelian category of finite-dimensional $\C$-representations of $Q$, and we assume in the following that all representations are finite-dimensional.

@@

  Since the map $ev_V$ is irreducible, $f$ is either a section or $h$ a retraction.  As $h$ is injective by the Snake Lemma, it cannot be a retraction. It follows that $f$ is a section and thus $g$ a retraction. Thus we find a morphism $g':X\to E$ such that $g\circ g'=\mathrm{id}_X$. We obtain
	$$\iota=\iota\circ\mathrm{id}_X=\iota\circ g\circ g'=\pi_{m+1}^V \circ h\circ g',$$i.e. $\iota$ factors through $P_{m+1}$,	and the claim follows from Lemma~\ref{le:preprojective subs}.
  %We proceed by induction on $m$.
  %When $m=1$, the dimension vector of $P_{m+1}^V$ is $(\codim_{\cH_m} V,1)$.
  %In particular, it is immediate that each proper subrepresentation of $P_{m+1}^V$ is isomorphic to $P_1^k$ for some $0\le k\le\codim_{\cH_m} V$.
